### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

  \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.

  \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.

>>>>

  \item We propose a novel method that automatically detects and analyzes the effect of each side-channel leakage site. Our analysis combines information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.

  \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of future work on quantifying the information leakage based on the fuzzing.
